ComparativePlots

### 2019-07-12 ComparativePlots.Rmd
changes to figures

MCC.BAMM.model.data %>% ggplot(aes(x = range.size.m2, y = 0, fill = ..x..))+
  geom_density_ridges_gradient(scale = 3, size = 0.05, gradient_lwd = 0.75)+
  scale_fill_distiller(palette = "BuPu", direction = 1, guide = F)+
  scale_x_log10()+
  theme_minimal()+
  scale_y_discrete(expand = c(0,0))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.line.y = element_blank(), 
        panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x.bottom = element_line())
```

@@

BAMM.scatter <- MCC.BAMM.model.data %>% ggplot(aes(y = mean.lambda, x = SDi, fill = ..x..))+
  # geom_point(data = restricted.data, aes(x = SDi, y = exp(MCC.DR)), color = "gray70")+
  geom_point(shape = 21, stroke = 0.35)+
  scale_fill_distiller(palette = "OrRd", direction = 1, guide = F)+
  scale_y_continuous(breaks = c(0.01,0.1, 1.0), limits = c(0.01, 7), trans = "log")+
  theme_bw()+
  xlab("Sexual Dichromatism")+
  ylab("Speciation Rate (BAMM)")+
    geom_abline(slope = MCC.Lambda.top[["coefficients"]][["SDi"]],
             intercept =  SDi.intercept.BAMM, 
             size = 1)+
  geom_abline(slope = min(BAMM.lambda.pgls.summary %>% 
                            filter(Parameter == "SDi") %>% 
                            select(Estimate)),
             intercept =  SDi.intercept.BAMM, 
             size = .75, 
             linetype = 2)+
  geom_abline(slope = max(BAMM.lambda.pgls.summary %>% 
                            filter(Parameter == "SDi") %>% 
                            select(Estimate)),
             intercept =  SDi.intercept.BAMM, 
             size = .75, 
             linetype = 2)+
    scale_x_continuous(expand = c(0,0.3))+
    theme(panel.grid = element_blank(),
          axis.line = element_line(),
          panel.border = element_blank(),
          plot.margin = unit(c(.5,.5,.5,.5), "cm"))

#Get more leasonable intercept for gls slope
SDi.intercept <- coef(gls(MCC.DR ~ SDi, data = restricted.data))[1]

DR.scatter <- restricted.data %>% ggplot(aes(y = exp(MCC.DR), x = SDi, fill = ..x..))+
  geom_point(shape = 21, stroke = 0.35)+
  scale_fill_distiller(palette = "OrRd", direction = 1, guide = F)+
  theme_bw()+
  scale_y_continuous(breaks = c(0.01,0.1, 1.0), limits = c(0.01, 7), trans = "log")+
  scale_x_continuous(expand = c(0,0.3))+
  xlab("Sexual Dichromatism")+
  ylab("Speciation Rate")+
  geom_smooth(method = "glm", se = F, color = "black", linetype = 5)+ 
    theme(panel.grid = element_blank(),
          axis.line = element_line(),
          panel.border = element_blank(),
          plot.margin = unit(c(.5,.5,.5,.5), "cm"))

Range.scatter <- restricted.data %>% ggplot(aes(y = exp(MCC.DR), x = range.size.m2, fill = ..x..))+
  geom_point(shape = 21, stroke = 0.35)+
  scale_fill_distiller(palette = "BuPu", direction = 1, guide = F, trans = "log")+
  theme_bw()+
  scale_y_continuous(breaks = c(0.01,0.1, 1.0), limits = c(0.01, 7), trans = "log")+
  scale_x_continuous(expand = c(0,0.3), trans = "log", breaks = c(1, 1*(10^7), 1*(10^10), 1*(10^13)))+
  xlab("Range Size")+
  ylab("Speciation Rate")+
    geom_smooth(method = "glm", se = F, color = "black", linetype = 5)+
    theme(panel.grid = element_blank(),
          axis.line = element_line(),
          panel.border = element_blank(),
          plot.margin = unit(c(.5,.5,.5,.5), "cm"))

BAMM.scatter
DR.scatter
Range.scatter
```

@@

# ggtree.plot <-gheatmap2(ggtree.plot, data = MCC.BAMM.model.data %>% select(SDi), width=0.05, colnames = FALSE, low = "orange", high = "red")

@@

```{r}
cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#d9ef8b",
           brewer.pal(n = 9, name = "YlGn")[4:9])
display.brewer.pal(n = 11, name = "RdYlGn")[4:11]
#cols <- c("#045a8d", "#74a9cf", "#ffd92f", "#d9f0a3", "#78c679", "#005a32")
#20 x 20 plots
ggtree.plot.dr <- ggtree(fortified.DR.tree, aes(color =  rate),
                      layout="fan", open.angle = 90, size = 0.175) + 
  xlim(-75, NA)+
  scale_colour_gradientn(colours = cols, 
                         #breaks = c(-4, -2, 1.75, 1.2),
                         guide = F) +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 18))

# ggtree.plot.dr <- gheatmap2(ggtree.plot.dr, data = MCC.BAMM.model.data %>% select(SDi), width=0.05, colnames = FALSE) + 
#   scale_fill_distiller(palette = "OrRd", direction = 1, na.value = "white", guide = guide_colorbar(direction = "horizontal", label.position = "bottom", barheight = 1.5, barwidth = 25, label.vjust = -0.5))+
#     theme(legend.position = "bottom",
#         legend.text = element_text(size = 18))
```

@@

>>>>

MCC.BAMM.model.data %>% ggplot(aes(x = range.size.m2, y = 0, fill = ..x..))+
  geom_density_ridges_gradient(scale = 3, size = 0.05, gradient_lwd = 0.75)+
  scale_fill_distiller(palette = "BuPu", direction = 1, guide = F)+
  scale_x_log10()+
  theme_minimal()+
  scale_y_discrete(expand = c(0,0))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.line.y = element_blank(), 
        panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x.bottom = element_line())

SS.subset %>% ggplot(aes(x = Sexual_selection_ppca, y = 0, fill = ..x..))+
  geom_density_ridges_gradient(scale = 3, size = 0.05, gradient_lwd = 0.75)+
  scale_fill_distiller(palette = "Greys", direction = 1, guide = F)+
  theme_minimal()+
  scale_y_discrete(expand = c(0,0))+
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.line.y = element_blank(), 
        panel.grid = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x.bottom = element_line())
```

@@

BAMM.scatter <- MCC.BAMM.model.data %>% ggplot(aes(y = mean.lambda, x = SDi, fill = ..x..))+
  # geom_point(data = restricted.data, aes(x = SDi, y = exp(MCC.DR)), color = "gray70")+
  geom_point(shape = 21, stroke = 0.35)+
  scale_fill_distiller(palette = "OrRd", direction = 1, guide = F)+
  scale_y_continuous(breaks = c(0.01,0.1, 1.0), limits = c(0.01, 7), trans = "log")+
  theme_bw()+
  xlab("Sexual Dichromatism")+
  ylab("Speciation Rate (BAMM)")+
    geom_abline(slope = MCC.Lambda.top[["coefficients"]][["SDi"]],
             intercept =  SDi.intercept.BAMM, 
             size = 1)+
  geom_abline(slope = min(BAMM.lambda.pgls.summary %>% 
                            filter(Parameter == "SDi") %>% 
                            select(Estimate)),
             intercept =  SDi.intercept.BAMM, 
             size = .75, 
             linetype = 2)+
  geom_abline(slope = max(BAMM.lambda.pgls.summary %>% 
                            filter(Parameter == "SDi") %>% 
                            select(Estimate)),
             intercept =  SDi.intercept.BAMM, 
             size = .75, 
             linetype = 2)+
    scale_x_continuous(expand = c(0,0.3))+
    theme(panel.grid = element_blank(),
          axis.line = element_line(),
          panel.border = element_blank(),
          plot.margin = unit(c(.5,.5,.5,.5), "cm"))
```

@@

 ggtree.plot <-gheatmap2(ggtree.plot, data = MCC.BAMM.model.data %>% left_join(SS.subset %>% select(TipLabel, Sexual_selection_ppca), by = "TipLabel") %>% select(Sexual_selection_ppca), width=0.05, colnames = FALSE, low = "grey90", high = "black")

@@

```{r}
cols <- c("#543005", "#8c510a", "#bf812d", "#dfc27d", "#d9ef8b",
           brewer.pal(n = 9, name = "YlGn")[4:9])
display.brewer.pal(n = 11, name = "RdYlGn")[4:11]
#cols <- c("#045a8d", "#74a9cf", "#ffd92f", "#d9f0a3", "#78c679", "#005a32")
#20 x 20 plots
ggtree.plot.dr <- ggtree(fortified.DR.tree, aes(color =  rate),
                      layout="fan", open.angle = 90, size = 0.175) + 
  xlim(-75, NA)+
  scale_color_distiller(palette = "YlGn", direction = 1, guide = F, trans = "log", breaks=c(0.05, 0.15, 0.5, 1.5))+
  theme(legend.position = "bottom",
        legend.text = element_text(size = 18))

# ggtree.plot.dr.1 <- gheatmap2(ggtree.plot.dr, data = MCC.BAMM.model.data %>% `rownames<-`(MCC.BAMM.model.data$TipLabel) %>% select(SDi), width=0.05, colnames = FALSE)  +
# scale_fill_distiller(palette = "OrRd", direction = 1, na.value = "white", guide = F)
# 
# ggtree.plot.dr.2 <- ggtree.plot.dr.1 + new_scale_fill() 
# ggtree.plot.dr.2 <- gheatmap2(ggtree.plot.dr.2, data = MCC.BAMM.model.data %>% `rownames<-`(MCC.BAMM.model.data$TipLabel) %>% select(SDi), width=0.05, colnames = FALSE)  +
# scale_fill_distiller(palette = "BuPu", direction = 1, na.value = "white", guide = F)
# 
# ggtree.plot.dr.3 <- ggtree.plot.dr.2 + new_scale_fill() 
# ggtree.plot.dr.3 <- gheatmap2(ggtree.plot.dr.3, data = MCC.BAMM.model.data %>% `rownames<-`(MCC.BAMM.model.data$TipLabel) %>% left_join(SS.subset %>% select(TipLabel, Sexual_selection_ppca), by = "TipLabel") %>% select(Sexual_selection_ppca), width=0.05, colnames = FALSE)  +
# scale_fill_distiller(palette = "Greys", direction = 1, na.value = "white", guide = F)

ggtree.plot.dr.3 <- gheatmap2(ggtree.plot.dr, data = MCC.BAMM.model.data %>% left_join(SS.subset %>% select(TipLabel, Sexual_selection_ppca), by = "TipLabel")%>% `rownames<-`(MCC.BAMM.model.data$TipLabel) %>% select(Sexual_selection_ppca), width=0.05, colnames = FALSE, low = "Grey90", high = "Black")

#     theme(legend.position = "bottom",
#         legend.text = element_text(size = 18))
# 
# ggtree.plot.dr.h <- gheatmap2(ggtree.plot.dr, data = MCC.BAMM.model.data %>% select(SDi), width=0.5, colnames = FALSE, low = "grey90", high = "black")

```{r}

Lepidothrix.coeruleocapilla.data <- restricted.data %>% filter(TipLabel == "Lepidothrix_coeruleocapilla")

@@

#Figure 1 in manuscript (filtered model results)

```{r, fig.height = 8, fig.width = 4, message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
library(Cairo)
library(data.table)

#Cols for plot: 
cols1 <- c("#8856a7", "#c6dbef")
cols2 <- c("#8856a7", "#fc8d59")

#Read in the 1000 tree summary df and the MCC tree model
DR.pgls.summary <- readRDS("data/DR.pgls.summary.rds")
MCC.DR.top <- readRDS('data/MCC.DR.top.rds')
MCC.DR.summary <-  data.frame(MCC.DR.top$coefficients,
                              confint(MCC.DR.top),
                              coef(summary(MCC.DR.top))[,2], #Std.Error
                              coef(summary(MCC.DR.top))[,3], #t-val
                              coef(summary(MCC.DR.top))[,4], #pval
                              MCC.DR.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% 
  tibble::rownames_to_column() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))

#Now plot this for Node Density (ND):

ND.pgls.summary <- readRDS("data/ND.pgls.summary.rds")
MCC.ND.top <- readRDS('data/MCC.ND.top.rds')
MCC.ND.summary <- data.frame(MCC.ND.top$coefficients,
                              confint(MCC.ND.top),
                              coef(summary(MCC.ND.top))[,2], #Std.Error
                              coef(summary(MCC.ND.top))[,3], #t-val
                              coef(summary(MCC.ND.top))[,4], #pval
                              MCC.ND.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% 
  tibble::rownames_to_column() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))

parameter_names <- c(
                    `bioclim4` = "Temperature Seasonality",
                    `log(range.size.m2)` = "Range Size (log-transformed)",
                    `NPP` = "NPP",
                    `PC1.LIG` = "Long-term Temperature Variation",
                    `residuals.PC1` = "Spatial Temperature Variation",
                    `SDi` = "Sexual Dichromatism"
                    )

DR.plot.sub <-DR.pgls.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")) %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  #geom_errorbarh(aes(xmin = LCI, xmax = UCI, colour = Parameter), position = position_jitter(seed = 1), height = 0)+
  geom_point(shape = 21, alpha = 0.25, size = 0.75, position = position_jitter(seed = 1))+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

DR.plot.sub <- DR.plot.sub + geom_errorbarh(data = MCC.DR.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), 
                 aes(xmin = LCI,
                     xmax = UCI, y = Parameter,
                     color = Parameter), 
                 height = 0, show.legend = F, 
                 position = position_nudge(y= -0.75))+

  geom_point(data = MCC.DR.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), 
             aes(x = Estimate, y = Parameter, fill = Parameter), 
             shape=21, color = "grey20",
             size = 3,
             position = position_nudge(y= -0.75)) +
  scale_y_discrete(expand = c(0.5,.5))+
  facet_wrap(~ Parameter, scales = "free", nrow = 6, labeller = as_labeller(parameter_names))+
  scale_fill_manual(values = cols1)+
  scale_color_manual(values = cols1)+
  theme(panel.grid.major.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 7),
        plot.title = element_text(hjust = 0.5),
        plot.margin=unit(c(.5,.5,.5,.5),"cm"))+
  ggtitle(expression(paste(lambda['DR'], sep = "")))

ND.plot.sub <-ND.pgls.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")) %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  geom_jitter(shape = 21, alpha = 0.25, size = 0.75)+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

ND.plot.sub <- ND.plot.sub + geom_errorbarh(data = MCC.ND.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), 
                 aes(xmin = LCI,
                     xmax = UCI, y = Parameter,
                     color = Parameter), 
                 height = 0, show.legend = F, 
                 position = position_nudge(y= -0.75))+

  geom_point(data = MCC.ND.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), 
             aes(x = Estimate, y = Parameter, fill = Parameter), 
             shape=21, color = "grey20",
             size = 3,
             position = position_nudge(y= -0.75)) +
  scale_y_discrete(expand = c(0.5,0.5))+
  facet_wrap(~ Parameter, scales = "free", nrow = 6, labeller = as_labeller(parameter_names))+
  scale_fill_manual(values = cols1)+
  scale_color_manual(values = cols1)+
  theme(panel.grid.major.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 7),
        plot.title = element_text(hjust = 0.5),
        plot.margin=unit(c(.5,.5,.5,.5),"cm"))+
  ggtitle(expression(paste(lambda['ND'], sep = "")))

BAMM.lambda.pgls.models <- readRDS("data/BAMM.lambda.pgls.models.rds")

BAMM.lambda.pgls.summary <- lapply(BAMM.lambda.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})

#Now plot this for Lambda

MCC.Lambda.top <- readRDS('data/MCC.Lambda.top.rds')
MCC.lambda.summary <- data.frame(MCC.Lambda.top$coefficients,
                              confint(MCC.Lambda.top),
                              coef(summary(MCC.Lambda.top))[,2], #Std.Error
                              coef(summary(MCC.Lambda.top))[,3], #t-val
                              coef(summary(MCC.Lambda.top))[,4], #pval
                              MCC.Lambda.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% 
  tibble::rownames_to_column() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))

BAMM.lambda.pgls.summary <- bind_rows(BAMM.lambda.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

  # for (x in unique(BAMM.lambda.pgls.summary$Parameter)[2:7]){
  #   filter(Parameter == x & between(Estimate, left = as.numeric(hpd.Lambda.top[1,x]), right = as.numeric(hpd.Lambda.top[2,x])))
  #   }

remove_outliers <- function(x, na.rm = TRUE, ...) {
  qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
  H <- 1.5 * IQR(x, na.rm = na.rm)
  y <- x
  y[x < (qnt[1] - H)] <- NA
  y[x > (qnt[2] + H)] <- NA
  y
}

BAMM.lambda.pgls.summary.RO <- data.table::dcast(BAMM.lambda.pgls.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), Estimate ~ Parameter, value.var = "Estimate")
BAMM.lambda.pgls.summary.RO$Estimate <- NULL
BAMM.lambda.pgls.summary.RO <- sapply(BAMM.lambda.pgls.summary.RO, function(x) {
  remove_outliers(x, na.rm = T)})
BAMM.lambda.pgls.summary.RO <-melt(BAMM.lambda.pgls.summary.RO) %>% na.omit()
BAMM.lambda.pgls.summary.RO$Var1 <- NULL
colnames(BAMM.lambda.pgls.summary.RO) <- c("Parameter", "Estimate")

BAMM.lambda.plot.sub <- BAMM.lambda.pgls.summary.RO %>%
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  geom_jitter(shape = 21, alpha = 0.25, size = 0.75)+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

BAMM.lambda.plot.sub <- BAMM.lambda.plot.sub + geom_errorbarh(data = MCC.lambda.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), 
                 aes(xmin = LCI,
                     xmax = UCI, y = Parameter,
                     color = Parameter), 
                 height = 0, show.legend = F, 
                 position = position_nudge(y= -0.75))+

  geom_point(data = MCC.lambda.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), 
             aes(x = Estimate, y = Parameter, fill = Parameter), 
             shape=21, color = "grey20",
             size = 3,
             position = position_nudge(y= -0.75)) +
  scale_y_discrete(expand = c(0.5,0.5))+
  facet_wrap(~ Parameter, scales = "free", nrow = 7, labeller = as_labeller(parameter_names))+
  scale_fill_manual(values = cols1)+
  scale_color_manual(values = cols1)+
  theme(panel.grid.major.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 7),
        plot.title = element_text(hjust = 0.5),
        plot.margin=unit(c(.5,.5,.5,.5),"cm"))+
  ggtitle(expression(paste(lambda['BAMM'], sep = "")))

#Figure for extinction

BAMM.mu.pgls.models <- readRDS("data/BAMM.mu.pgls.models.rds")

BAMM.mu.pgls.summary <- lapply(BAMM.mu.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})

BAMM.mu.pgls.summary <- bind_rows(BAMM.mu.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

#Now plot this for Lambda

MCC.Mu.top <- readRDS('data/MCC.Mu.top.rds')
MCC.mu.summary <- data.frame(MCC.Mu.top$coefficients,
                              confint(MCC.Mu.top),
                              coef(summary(MCC.Mu.top))[,2], #Std.Error
                              coef(summary(MCC.Mu.top))[,3], #t-val
                              coef(summary(MCC.Mu.top))[,4], #pval
                              MCC.Mu.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% 
  tibble::rownames_to_column() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))

#Get rid of outliers
BAMM.mu.pgls.summary.RO <- data.table::dcast(BAMM.mu.pgls.summary %>% dplyr::select(Parameter,Estimate) %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), Estimate ~ Parameter, value.var = "Estimate")
BAMM.mu.pgls.summary.RO$Estimate <- NULL
BAMM.mu.pgls.summary.RO <- sapply(BAMM.mu.pgls.summary.RO, function(x) {
  remove_outliers(x, na.rm = T)})
BAMM.mu.pgls.summary.RO <-melt(BAMM.mu.pgls.summary.RO) %>% na.omit()
BAMM.mu.pgls.summary.RO$Var1 <- NULL
colnames(BAMM.mu.pgls.summary.RO) <- c("Parameter", "Estimate")

BAMM.Mu.plot.sub <-BAMM.mu.pgls.summary.RO %>%
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  geom_jitter(shape = 21, alpha = 0.25, size = 0.75)+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

BAMM.Mu.plot.sub <- BAMM.Mu.plot.sub + geom_errorbarh(data = MCC.mu.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), 
                 aes(xmin = LCI,
                     xmax = UCI, y = Parameter,
                     color = Parameter), 
                 height = 0, show.legend = F, 
                 position = position_nudge(y= -0.75))+

  geom_point(data = MCC.mu.summary %>% filter(Parameter %in% c("log(range.size.m2)", "SDi")), 
             aes(x = Estimate, y = Parameter, fill = Parameter), 
             shape=21, color = "grey20",
             size = 3,
             position = position_nudge(y= -0.75)) +
  scale_y_discrete(expand = c(0.5,0.5))+
  facet_wrap(~ Parameter, scales = "free", nrow = 7, labeller = as_labeller(parameter_names))+
  scale_fill_manual(values = cols1)+
  scale_color_manual(values = cols1)+
  theme(panel.grid.major.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 7),
        plot.title = element_text(hjust = 0.5),
        plot.margin=unit(c(.5,.5,.5,.5),"cm"))+
  ggtitle(expression(paste(mu['BAMM'], sep = "")))

Subset.DR.pgls.summary <- readRDS("data/Subset.DR.pgls.summary.rds")
Subset.ND.pgls.summary <- readRDS("data/Subset.ND.pgls.summary.rds")

### MCC
Subset.MCC.DR.top <- readRDS('data/Subset.MCC.DR.top.rds')

Subset.MCC.DR.summary <- data.frame(Subset.MCC.DR.top$coefficients,
                              confint(Subset.MCC.DR.top),
                              coef(summary(Subset.MCC.DR.top))[,2], #Std.Error
                              coef(summary(Subset.MCC.DR.top))[,3], #t-val
                              coef(summary(Subset.MCC.DR.top))[,4], #pval
                              Subset.MCC.DR.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% tibble::rownames_to_column()

colnames(Subset.MCC.DR.summary) <- c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name")

parameter_names <- c(
                    `bioclim4` = "Temperature Seasonality",
                    `log(range.size.m2)` = "Range Size (log-transformed)",
                    `NPP` = "NPP",
                    `PC1.LIG` = "Long-term Temperature Variation",
                    `residuals.PC1` = "Spatial Temperature Variation",
                    `Sexual_selection_ppca` = "Sexual Selection"
                    )

Subset.DR.pgls.summary$Parameter = factor(Subset.DR.pgls.summary$Parameter, levels=c('bioclim4','log(range.size.m2)','NPP','PC1.LIG', 'residuals.PC1', 'Sexual_selection_ppca'))

Subset.MCC.DR.summary$Parameter = factor(Subset.MCC.DR.summary$Parameter, levels=c('bioclim4','log(range.size.m2)','NPP','PC1.LIG', 'residuals.PC1', 'Sexual_selection_ppca'))

Subset.DR.plot.sub <-Subset.DR.pgls.summary %>% filter(Parameter %in% c("log(range.size.m2)", "Sexual_selection_ppca")) %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  geom_jitter(shape = 21, alpha = 0.25, size = 0.75)+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

Subset.DR.plot.sub <- Subset.DR.plot.sub + geom_errorbarh(data = Subset.MCC.DR.summary %>% filter(Parameter %in% c("log(range.size.m2)", "Sexual_selection_ppca")), 
                 aes(xmin = LCI,
                     xmax = UCI, y = Parameter,
                     color = Parameter), 
                 height = 0, show.legend = F, 
                 position = position_nudge(y= -0.75))+

  geom_point(data = Subset.MCC.DR.summary %>% filter(Parameter %in% c("log(range.size.m2)", "Sexual_selection_ppca")), 
             aes(x = Estimate, y = Parameter, fill = Parameter), 
             shape=21, color = "grey20",
             size = 3,
             position = position_nudge(y= -0.75)) +
  scale_y_discrete(expand = c(0.5,.5))+
  facet_wrap(~ Parameter, scales = "free", nrow = 6, labeller = as_labeller(parameter_names))+
  scale_fill_manual(values = cols2)+
  scale_color_manual(values = cols2)+
  theme(panel.grid.major.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 7),
        plot.title = element_text(hjust = 0.5),
        plot.margin=unit(c(.5,.5,.5,.5),"cm"))+
  ggtitle(expression(paste(lambda['DR'], sep = "")))

####################################
#For ND

Subset.MCC.ND.top <- readRDS('data/Subset.MCC.ND.top.rds')

Subset.MCC.ND.summary <- data.frame(Subset.MCC.ND.top$coefficients,
                              confint(Subset.MCC.ND.top),
                              coef(summary(Subset.MCC.ND.top))[,2], #Std.Error
                              coef(summary(Subset.MCC.ND.top))[,3], #t-val
                              coef(summary(Subset.MCC.ND.top))[,4], #pval
                              Subset.MCC.ND.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% tibble::rownames_to_column()

colnames(Subset.MCC.ND.summary) <- c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name")

Subset.ND.pgls.summary$Parameter = factor(Subset.ND.pgls.summary$Parameter, levels=c('bioclim4','log(range.size.m2)','NPP','PC1.LIG', 'residuals.PC1', 'Sexual_selection_ppca'))

Subset.MCC.ND.summary$Parameter = factor(Subset.MCC.ND.summary$Parameter, levels=c('bioclim4','log(range.size.m2)','NPP','PC1.LIG', 'residuals.PC1', 'Sexual_selection_ppca'))

Subset.ND.plot.sub <-Subset.ND.pgls.summary %>% filter(Parameter %in% c("log(range.size.m2)", "Sexual_selection_ppca")) %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  geom_jitter(shape = 21, alpha = 0.25, size = 0.75)+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

Subset.ND.plot.sub <- Subset.ND.plot.sub + geom_errorbarh(data = Subset.MCC.ND.summary %>% filter(Parameter %in% c("log(range.size.m2)", "Sexual_selection_ppca")), 
                 aes(xmin = LCI,
                     xmax = UCI, y = Parameter,
                     color = Parameter), 
                 height = 0, show.legend = F, 
                 position = position_nudge(y= -0.75))+

  geom_point(data = Subset.MCC.ND.summary %>% filter(Parameter %in% c("log(range.size.m2)", "Sexual_selection_ppca")), 
             aes(x = Estimate, y = Parameter, fill = Parameter), 
             shape=21, color = "grey20",
             size = 3,
             position = position_nudge(y= -0.75)) +
  scale_y_discrete(expand = c(0.5,.5))+
  facet_wrap(~ Parameter, scales = "free", nrow = 6, labeller = as_labeller(parameter_names))+
  scale_fill_manual(values = cols2)+
  scale_color_manual(values = cols2)+
  theme(panel.grid.major.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 7),
        plot.title = element_text(hjust = 0.5),
        plot.margin=unit(c(.5,.5,.5,.5),"cm"))+
  ggtitle(expression(paste(lambda['ND'], sep = "")))

######################

#For Lambda
Subset.BAMM.lambda.pgls.models <- readRDS("data/Subset.BAMM.lambda.pgls.models.rds")
Subset.MCC.Lambda.top <- readRDS('data/Subset.MCC.Lambda.top.rds')

Subset.Lambda.pgls.summary <- lapply(Subset.BAMM.lambda.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})

Subset.Lambda.pgls.summary <- bind_rows(Subset.Lambda.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

#MCC

Subset.MCC.Lambda.summary <- data.frame(Subset.MCC.Lambda.top$coefficients,
                              confint(Subset.MCC.Lambda.top),
                              coef(summary(Subset.MCC.Lambda.top))[,2], #Std.Error
                              coef(summary(Subset.MCC.Lambda.top))[,3], #t-val
                              coef(summary(Subset.MCC.Lambda.top))[,4], #pval
                              Subset.MCC.Lambda.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% tibble::rownames_to_column()

colnames(Subset.MCC.Lambda.summary) <- c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name")

Subset.Lambda.pgls.summary$Parameter = factor(Subset.Lambda.pgls.summary$Parameter, levels=c('bioclim4','log(range.size.m2)','NPP','PC1.LIG', 'residuals.PC1', 'Sexual_selection_ppca'))

Subset.MCC.Lambda.summary$Parameter = factor(Subset.MCC.Lambda.summary$Parameter, levels=c('bioclim4','log(range.size.m2)','NPP','PC1.LIG', 'residuals.PC1', 'Sexual_selection_ppca'))

Subset.Lambda.pgls.summary.RO <- data.table::dcast(Subset.Lambda.pgls.summary %>% filter(Parameter %in% c("log(range.size.m2)", "Sexual_selection_ppca")), Estimate ~ Parameter, value.var = "Estimate")
Subset.Lambda.pgls.summary.RO$Estimate <- NULL
Subset.Lambda.pgls.summary.RO <- sapply(Subset.Lambda.pgls.summary.RO, function(x) {
  remove_outliers(x, na.rm = T)})
Subset.Lambda.pgls.summary.RO <-melt(Subset.Lambda.pgls.summary.RO) %>% na.omit()
Subset.Lambda.pgls.summary.RO$Var1 <- NULL
colnames(Subset.Lambda.pgls.summary.RO) <- c("Parameter", "Estimate")

Subset.Lambda.plot.sub <-Subset.Lambda.pgls.summary.RO %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  geom_jitter(shape = 21, alpha = 0.25, size = 0.75)+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

Subset.Lambda.plot.sub <- Subset.Lambda.plot.sub + geom_errorbarh(data = Subset.MCC.Lambda.summary %>% filter(Parameter %in% c("log(range.size.m2)", "Sexual_selection_ppca")), 
                 aes(xmin = LCI,
                     xmax = UCI, y = Parameter,
                     color = Parameter), 
                 height = 0, show.legend = F, 
                 position = position_nudge(y= -0.75))+
